%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Verification Engineer} % Job title
{RDA} % Organization
{Beijing} % Location
{Nov. 2014 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Independently set up UVM verification environment based on Constrained-random stimulus, and found several bugs which are hard to capture for direct cases in power management unit.}
\item {Added a small verification environment based on UVM, and built cases to verify power-domain controls for SOC level.}
\item {Helped to build SOC level environment based on MIPS/ARM core, and supply common component for direct cases in C, for example, linker script, printf function implement and interrupt register function etc.}
\item {Built the register flow script to generate UVM register model, C header file and documnets in several format-PDF, WORD, and HTML, depending on XML input file.}
\item {Built scripts for generating ready-to-go UVM-based unit test environment depending on XML input file.}
\item {Maintained the simulation automation script for common use, and supplied regression script for LSF jobs control and results statistics. Both Cadence VManager version and self-developed version are given.}
\item {Supplied irun simulation environment based on Multi-Snapshot Incremental Elaboration to reduce the compiling time for SOC team. The elaboration time during compiling is reduced to 30 minutes from 6 hours in netlist simulation phase.}
\item {Built up database for HAPS(FPGA platform) and Zebu(Emulation platform), which is for IP verification and software development.}
\end{cvitems}
}


%------------------------------------------------    

\cventry
{ASIC Flow Engineer} % Job title
{Innofidei} % Organization
{Beijing} % Location
{Aug. 2012 - Nov. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Synthesis, LEC, Crossing-Domain Check and Power Analysis.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{ASIC Design Engineer} % Job title
{Hisilicon} % Organization
{Beijing} % Location
{July. 2008 - Aug. 2012} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {In charge of designing a Linear Table search module, releasing document and writing RTL codes.}
\item {In charge of vendor's DDR PHY simulation, including configuration and training procedure.}
\item {Helped to chip bring up test, to develop ECO Tcl script and work-around method based on software.}
\item {Independently worked on FPGA prototype verification, including resources estimation, releasing scaled-down version, partition and implementation.}
\item {In charge of designing an Exact-Matched algorithm search module, and helping the timing closure with backend team.}
\end{cvitems} 
}

%------------------------------------------------

\end{cventries}